\documentclass[11pt]{article}

\usepackage[margin=1.1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage{xcolor}
\definecolor{linkblue}{RGB}{25,60,120}
\usepackage[colorlinks=true,linkcolor=linkblue,citecolor=linkblue,urlcolor=linkblue]{hyperref}

\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{claim}{Claim}
\newtheorem{remark}{Remark}

\newcommand{\F}{\mathbb{F}}
\newcommand{\Ftwo}{\F_2}
\newcommand{\Fsixteen}{\F_{16}}
\newcommand{\Ftag}{\F_{2^{128}}}
\newcommand{\shake}{\mathsf{SHAKE256}}
\newcommand{\ctx}{\mathsf{ctx}}
\newcommand{\Spre}{\mathsf{SPre}}
\newcommand{\enc}{\mathsf{enc}_{64}}
\newcommand{\Cred}{\mathsf{C}}
\newcommand{\Null}{\mathsf{N}}
\newcommand{\Def}{\mathsf{D}}
\newcommand{\adv}{\mathcal{A}}

\title{VOLE-ACT: Post-Quantum Anonymous Credit Tokens\\
from VOLE-in-the-Head and MAYO}
\author{Samuel Schlesinger}
\date{July 2026\\[0.5em]\normalsize Research draft --- definitions and analysis are stated as targets;\\
no complete security reduction is claimed}

\begin{document}
\maketitle

\begin{abstract}
Anonymous credit tokens let an issuer grant a client a hidden, spendable
balance: the client can later redeem credits unlinkably, each redemption
consumes a one-time nullifier and returns a fresh token on the remaining
balance. Classical constructions rest on discrete-logarithm-style algebra ---
blind or randomizable signatures, algebraic MACs, Sigma protocols --- none of
which survives a quantum adversary. We present VOLE-ACT, a post-quantum
instantiation of the Katz--Schlesinger anonymous-credit design~\cite{KS}
whose entire symmetric layer is Keccak and whose only algebraic assumption
concerns the multivariate-quadratic (whipped MAYO) trapdoor. The central
idea is to \emph{avoid blindness entirely}: the issuer signs a revealed
SHAKE256 commitment digest whose preimage stays hidden, and possession of
the signature is later proven in zero knowledge inside a VOLE-in-the-Head
proof system that is native to exactly the two ingredients that must be
proven --- Keccak (a Boolean circuit) and MAYO verification (a quadratic
system over $\Fsixteen \subseteq \Ftag$). We give syntax and security
definitions for anonymous credit tokens, the construction --- including a
degree-16 Keccak checkpointing technique that commits the permutation state
only every four rounds, and a batched quadratic-system constraint for
whipped MQ verification --- and a security analysis that states its
assumptions (an adaptive one-more-preimage property of the whipped map; an
ideal-XOF model) and its concrete attack ceilings explicitly. A Rust
research prototype achieves 19--20\,ms proving and 6.5--8\,ms issuer
verify-and-sign (proof verification plus MAYO preimage sampling) per spend,
with 53\,KiB proofs and 283-byte tokens.
\end{abstract}

\section{Introduction}

An anonymous credit token system has one issuer and many clients. The issuer
grants a client a public number of credits; the client can later spend part of
that balance without revealing which issuance --- or which earlier spend ---
produced the token being presented. Each accepted spend consumes a one-time
nullifier (preventing double spending) and returns a fresh token carrying the
remaining balance. The functionality generalizes anonymous tokens in the
Privacy Pass style~\cite{PrivacyPass} from unit tokens to stateful balances,
and specializes keyed-verification anonymous
credentials~\cite{CMZ14} to a single numeric attribute with exact arithmetic.

Classically this is well-trodden ground: blind signatures~\cite{Chaum82},
CL~signatures~\cite{CL01}, algebraic MACs~\cite{CMZ14} and their pairing-based
relatives give compact, efficient constructions. All of them lean on the
algebraic structure of discrete-log or pairing groups, both for the signature
and for the efficient zero-knowledge presentation protocol. Neither survives
a quantum adversary. The natural repair --- a post-quantum \emph{blind}
signature --- remains an active and unsettled research area in which several
early lattice-based proposals required substantial revision after
cryptanalysis; we prefer a design that does not need blindness at all.

\paragraph{The core idea: sign a digest, hide the preimage.}
VOLE-ACT, following the Katz--Schlesinger design~\cite{KS}, sidesteps
blindness. A credential is a short XOF stream
\[
X \;=\; \shake(\text{domain} \,\|\, \ctx \,\|\, \kappa \,\|\, \enc(b) \,\|\, \rho),
\]
over a client-chosen 256-bit nullifier key $\kappa$, public balance $b$, and
256-bit hiding nonce $\rho$. The first $4m$ bits of $X$ form the
\emph{commitment digest} $\Cred \in \Fsixteen^m$; the next 256 bits form the
\emph{nullifier} $\Null$. At issuance the client \emph{reveals} $\Cred$ and
proves in zero knowledge that it is well-formed for the public balance $b$;
the issuer then computes an ordinary MAYO preimage
$\sigma \gets \Spre(\mathsf{sk}, \Cred)$ and returns it. Nothing is blind:
the issuer sees exactly the digest it signs. Unlinkability comes later --- at
spend time the client proves \emph{in zero knowledge} that it knows
$(\sigma, \kappa, b, \rho)$ with $P^\ast(\sigma) = \Cred(\kappa,b,\rho)$,
revealing only the nullifier $\Null$, the public spend amount, and a fresh
commitment digest $\Cred'$ for the successor token. The signature and the
signed digest are never shown again, so there is nothing to link. The
unrevealed suffix of $X$ is treated as pseudorandom given its prefix, which
is what makes the nullifier unlinkable to the issuance in which the issuer
saw $\Cred$.

This pattern reduces the required primitives to (i) a post-quantum trapdoor
map whose \emph{verification} is cheap inside a proof system, and (ii) a
post-quantum zero-knowledge proof system that is efficient on
\emph{hash-heavy Boolean} statements. The pairing of MAYO with
VOLE-in-the-Head is unusually harmonious on both counts:

\begin{itemize}
  \item \textbf{MAYO}~\cite{Beullens21,MAYOspec} verification evaluates a
  public multivariate quadratic map over $\Fsixteen$. Since
  $\Fsixteen$ embeds as a subfield of the proof system's tag field
  $\Ftag$, the whole verification equation becomes a single batched
  \emph{quadratic system} constraint in the proof --- no bit decomposition,
  no modular arithmetic emulation.
  \item \textbf{VOLE-in-the-Head}~\cite{VOLEitH,FAEST} proof systems commit
  witness \emph{bits} and prove Boolean and low-degree relations at
  QuickSilver~\cite{QuickSilver,Wolverine} cost: linear gates are free, and
  the entire batch of polynomial constraints of maximum degree $d$ is checked
  with $d$ published $\Ftag$ elements. Keccak --- the only hash used
  anywhere --- is the friendliest possible circuit for such a system: its
  round function is degree 2.
\end{itemize}

\paragraph{Contributions.}
(1)~Syntax and game-based security definitions for anonymous credit tokens
with issuer-settled (\emph{deferred-return}) spends
(Section~\ref{sec:definitions}), including a candidate semi-formal
statement of the assumption the issuer's preimage-oracle role forces: an
adaptive \emph{one-more-preimage} property of the whipped MAYO map.
(2)~A post-quantum construction from that assumption plus an ideal XOF
(Section~\ref{sec:scheme}): one XOF stream yielding both commitment and
nullifier; a typed two-format token state machine; and a deferred-return
settlement in which the issuer selects a bounded return only \emph{after}
verifying the spend proof, bound by a nested hash.
(3)~Proof-circuit techniques (Section~\ref{sec:circuit}): \emph{degree-16
Keccak checkpointing}, committing the permutation state only every four
rounds and quartering the dominant witness cost by spending the proof
system's polynomial-degree budget; and a batched quadratic-system constraint
expressing whipped MQ verification over shared product terms, folded by
verifier randomness.
(4)~A security analysis (Section~\ref{sec:security}) that is explicit about
its conditional status, its concrete error terms, and its generic attack
ceilings --- including a $2^{256/3}$-query quantum collision bound on the
credential digest.
(5)~Evidence of practicality: a Rust research prototype
(Section~\ref{sec:performance}) with 19--20\,ms spend proving, 6.5--8\,ms
issuer verify-and-sign, 53\,KiB compact proofs, and 283-byte tokens.

\section{Preliminaries}

\subsection{Notation}
$\lambda = 128$ throughout. $\Ftwo$, $\Fsixteen = \Ftwo[x]/(x^4{+}x{+}1)$ and
$\Ftag = \Ftwo[x]/(x^{128}{+}x^7{+}x^2{+}x{+}1)$ are the Boolean, MAYO, and
tag fields; $\iota : \Fsixteen \hookrightarrow \Ftag$ is the
protocol-specified field embedding (the subfield is unique; the embedding is
fixed deterministically, with the reduction polynomial family used by
FAEST~\cite{FAEST}). $\shake$ is used for every PRG, commitment, and
Fiat--Shamir hash, always with prefix-free domain separation and
fixed-width or length-framed inputs~\cite{FIPS202}. $\enc(\cdot)$ is 64-bit
little-endian encoding. $\kappa$ denotes the client's nullifier key, $h$ a
GGM tree depth, and $k_w$ MAYO's whipping parameter.

\subsection{VOLE-based zero knowledge and VOLE-in-the-Head}
\label{sec:voleith}

In VOLE-based ZK~\cite{Wolverine,QuickSilver}, the prover holds, for each
witness bit $u_t \in \{0,1\}$, a \emph{tag} $V_t \in \Ftag$, and the verifier
holds a global secret $\Delta \in \Ftag$ and per-coordinate \emph{keys}
\[
K_t \;=\; V_t + u_t \cdot \Delta ,
\]
a vector oblivious linear evaluation (VOLE) correlation. Wires are affine
combinations of committed bits and are linearly homomorphic for free. A
multiplication (degree-2) constraint $a \cdot b = c$ is checked
QuickSilver-style: the verifier forms $B = K_a K_b + \Delta K_c$, which the
prover can match with a degree-1 polynomial in $\Delta$ exactly when the
constraint holds; a random linear combination with challenge weights
$\chi_i$ batches all constraints into one polynomial identity checked at
$\Delta$. The generalization to degree-$d$ polynomial constraints costs
$d$ published coefficients and $d-1$ random VOLE masks in total for the whole
batch.

VOLE-in-the-Head~\cite{VOLEitH} makes this \emph{publicly verifiable and
non-interactive}: the prover generates the VOLE correlation itself from
$\tau$ GGM~\cite{GGM86} seed trees of depth $h$ (with $\tau \cdot h =
\lambda$), commits to all $2^h$ leaves of each tree with an all-but-one
vector commitment, and the Fiat--Shamir challenge $\Delta$ selects, per tree,
one leaf that stays hidden; the remaining leaves are opened and the verifier
recomputes its keys. Soundness comes from the hidden leaf; zero knowledge
from the fact that the opened leaves are exactly what the verifier can
recompute anyway. Our instantiation follows the hardening of
FAEST~\cite{FAEST} and ``One Tree to Rule Them All''~\cite{OneTree}: every
PRG and commitment call binds a per-proof $2\lambda$-bit salt, a per-tree
derived salt, and the exact tree position, preventing the known multi-target
and multi-instance amortization attacks on the 128-bit seeds; small-field
consistency across the $\tau$ trees uses public corrections re-based onto
one shared $u$-vector, in the style of SoftSpokenOT~\cite{SoftSpoken}.

Three parameter profiles trade proof size against tree-expansion work:
\emph{compact} $(\tau,h) = (16,8)$, \emph{balanced} $(32,4)$, and
\emph{low-latency} $(64,2)$. Each opened proof reveals $\tau$ tree openings
of $h$ sibling seeds, so proofs shrink as $h$ grows while the prover expands
$\tau \cdot 2^h$ leaves.

\paragraph{The consistency check must be a matrix hash.}
Because each tree contributes only $h$ bits of $\Delta$, a cheating prover
who mangles one tree's correction data is caught by a per-tree check only
with probability $1 - 2^{-h}$ --- as low as $3/4$ for $h=2$. The
construction therefore applies a $128$-row \emph{column-wise linear
universal hash} to the entire tag matrix (two independent polynomial
evaluations combined with random weights, plus a one-time-pad block), so that
any inconsistency survives into the check equation except with probability
$\approx 2^{-\lambda}$ plus small degree-dependent evaluation terms,
regardless of the chunk structure (an exact bound is part of the outstanding
analysis). A scalar hash in place of the matrix hash is a real soundness bug
we caught during development; we flag it because the failure is silent and
parameter-dependent.

\subsection{MAYO}
\label{sec:mayo}

MAYO~\cite{Beullens21,MAYOspec} is an oil-and-vinegar~\cite{UOV} trapdoor
map: a public quadratic map $P : \Fsixteen^{n} \to \Fsixteen^{m}$
vanishing on a secret $o$-dimensional oil space, with $o < m$ deliberately
too small for direct Kipnis--Shamir-style attacks; the ``whipping''
construction evaluates $k_w$ correlated copies to stretch the oil space, so
the effective (whipped) public map is
$P^\ast : \Fsixteen^{k_w n} \to \Fsixteen^{m}$, matching the notation of the
MAYO literature. The trapdoor samples preimages
$\sigma$ with $P^\ast(\sigma) = y$ for arbitrary targets $y$; this
\emph{hash-then-invert} usage (rather than MAYO's message-signing API) is
exactly what the scheme needs. We use the round-2 parameter set
MAYO$_2$: $(n,m,o,k_w) = (81,64,17,4)$, so $\sigma \in \Fsixteen^{324}$
(162 bytes) and targets are $m = 64$ nibbles (32 bytes). We note the risk
posture explicitly: multivariate trapdoors have a difficult history ---
Rainbow fell to a practical attack in 2022~\cite{Beullens22} --- and MAYO's
whipping is comparatively young. The design compartmentalizes this risk:
a MAYO break forges credentials but is not expected to deanonymize past
transactions, whose privacy rests only on the hash-based layer
(Claim~\ref{claim:anon}).

For the proof circuit, the whipped map is expanded once per public key into
$m$ upper-triangular forms $G_a \in \Fsixteen^{k_w n \times k_w n}$ with
$P^\ast(\sigma)_a = \sigma^{\!\top} G_a\, \sigma$; the circuit then proves
$m$ quadratic equations over the \emph{same} $\binom{k_w n + 1}{2}$ product
terms (Section~\ref{sec:quadsys}).

\section{Definitions and assumptions}
\label{sec:definitions}

We state the syntax and the security games the eventual analysis must
target. The games are given at a semi-formal level: they pin down the
adversary's interfaces, win conditions, and the leakage the definitions
deliberately permit; a fully formal treatment (in particular of concurrent
sessions and adaptive corruptions) is left to the reduction effort.

\begin{definition}[Anonymous credit token scheme]
\label{def:syntax}
An \emph{anonymous credit token scheme} with balance space
$\{0,\dots,2^{64}{-}1\}$ is a tuple of interactive algorithms
\[
(\mathsf{Setup},\ \mathsf{Issue},\ \mathsf{Spend},\
\mathsf{SpendDeferred},\ \mathsf{VerifyToken})
\]
between an issuer and clients:
\begin{itemize}
  \item $\mathsf{Setup}(1^\lambda, \mathsf{app}) \to
  (\mathsf{sk}, \mathsf{pk}, \ctx)$: generates the issuer trapdoor, public
  key, and a context binding the key, application domain, parameter set,
  and protocol version.
  \item $\mathsf{Issue}\langle \mathrm{C}(\mathsf{pk}, b),
  \mathrm{I}(\mathsf{sk}, b) \rangle \to T$ (public balance $b$): the client
  obtains a \emph{direct token} $T$ of effective balance $b$, or aborts.
  \item $\mathsf{Spend}\langle \mathrm{C}(\mathsf{pk}, T, s),
  \mathrm{I}(\mathsf{sk}) \rangle \to T'$ (public amount $s$): consumes
  $T$'s nullifier and yields a direct token $T'$ of effective balance
  $\mathsf{bal}(T) - s$, or aborts.
  \item $\mathsf{SpendDeferred}\langle \mathrm{C}(\mathsf{pk}, T, s),
  \mathrm{I}(\mathsf{sk}, t') \rangle \to T'$: as $\mathsf{Spend}$, except
  the issuer selects a return $t' \le s$ \emph{after} verifying the
  client's proof; the output is a \emph{deferred-return token} of effective
  balance $\mathsf{bal}(T) - s + t'$.
  \item $\mathsf{VerifyToken}(\mathsf{pk}, T) \to \{0,1\}$: local client
  authentication of a decoded token. Tokens are never sent as
  presentations; only spend transcripts are.
\end{itemize}
Both spend operations accept either token format as input; the four
input/output transitions carry distinct type tags bound into their
transcripts.
\end{definition}

\begin{definition}[Correctness, informal]
\label{def:correctness}
Consider an experiment in which an environment drives an honest issuer and
honest clients to build a DAG of tokens: roots arise from
$\mathsf{Issue}(b)$ and every internal node from spending a
not-yet-spent node, with amounts respecting balances. The scheme is correct
if, except with negligible probability, no honest operation aborts, every
client-side authentication check passes, every output balance obeys the
equations of Definition~\ref{def:syntax}, distinct accepted inputs yield
distinct nullifiers, and exact retransmission of a request returns the
stored response rather than a new node.
\end{definition}

\begin{definition}[Fiscal soundness game]
\label{def:fiscal}
The adversary $\adv$ controls all clients and interacts, over the whole
experiment, with an honest issuer through three oracles:
$\mathsf{ISSUE}(b)$, whose accepted calls are externally authorized and
record $b$; $\mathsf{SPEND}(\cdot)$; and $\mathsf{SPENDDEF}(\cdot, t')$,
where $\adv$ names the desired return and the oracle enforces $t' \le s$
and reports the applied $t'$ in its output (in the real system $t'$ is
issuer policy; letting $\adv$ choose it is conservative). Rejected calls
record nothing, and accounting is per \emph{logical spend event}: each
first durable consumption of a nullifier creates one record, an exact
retransmission of the same request contributes zero additional redemption
and returns the originally recorded response (including the original
$t'$), and conflicting reuse of a consumed nullifier is rejected. External
redemption of value must be idempotent at the same boundary. Define the
\emph{net redeemed value} of a logical ordinary spend of public amount $s$
as $s$, and of a logical deferred spend as $s - t'$. $\adv$ wins if at any
point during the experiment
\[
\sum_{\text{accepted spends}} \text{net redeemed value}
\;>\;
\sum_{\text{accepted issuances}} b .
\]
The scheme is fiscally sound if every efficient $\adv$ wins with negligible
probability.
\end{definition}

\begin{remark}[Redemption-only is without loss of generality]
The win condition counts only \emph{redeemed} value, not outstanding
spendable balances, so an attack that merely \emph{forks} a token into two
live successors has not yet won. It extends to a win at will: any
adversary holding more spendable value than the invariant allows simply
continues querying $\mathsf{SPEND}$ to cash the excess out, and the game
runs for the whole experiment. Formally, redemption-only soundness is
equivalent to the ledger invariant of the design document
(redeemed value $+$ live independently spendable value $\le$ issued value)
up to this cash-out reduction, which is the statement a full analysis
should prove as a lemma rather than assume.
\end{remark}

\begin{definition}[Spend anonymity game, single challenge]
\label{def:anon}
The adversary $\adv$ plays a malicious issuer. It first outputs arbitrary
public-key bytes; the challenger parses and validates them with the
scheme's canonical decoder (the game proceeds only on a valid parse) and
recomputes $\ctx$ itself exactly as $\mathsf{Setup}$ prescribes; the key
and context are fixed for the remainder of the game. The challenger then
operates honest clients, which perform every client-side authentication
check and abort on failure; $\adv$ executes the issuer side of all
sessions, sees all transcripts, and may abort any session (an aborted
session yields no token).

$\adv$ directs the creation of honest tokens through arbitrary
issuance/spend histories, then designates two \emph{authenticated, unspent}
tokens $T_0, T_1$ of the same credential kind and \emph{equal effective
balance}, and a challenge: a spend of public amount $s$ valid for both,
with a fixed settlement mode. The challenger executes the challenge on
$T_\beta$ for $\beta \gets \{0,1\}$ and hands $\adv$ the transcript
(including issuer-visible aborts, which $\adv$ may induce). Thereafter
$T_0$, $T_1$, and the challenge's successor token are \emph{retired}: no
further oracle use, by either party, involves them. $\adv$ may continue
directing operations on unrelated tokens, then outputs $\beta'$ and wins
if $\beta' = \beta$; the scheme is spend-anonymous if
$|\Pr[\beta' = \beta] - 1/2|$ is negligible.

The same-kind, same-mode, same-amount, equal-balance restrictions reflect
leakage the syntax makes public by design. Retiring the \emph{candidates}
closes the immediate distinguisher: replaying a candidate would reveal
$\beta$ through nullifier reuse. Retiring the \emph{successor} (whose
balance is the same in both worlds, given equal candidate balances) is
not needed against that attack; it isolates the definition to a single
challenged transcript rather than smuggling in a compositional guarantee
about continued use. A chain definition (hidden, permuted token handles
with identical admissible continuations) is the natural strengthening and
is left open. Section~\ref{sec:security} discusses the metadata any
deployment leaks outside this game.
\end{definition}

\begin{assumption}[Adaptive one-more preimage for whipped MAYO,
semi-formal]
\label{ass:omp}
Let $(\mathsf{sk}, \mathsf{pk})$ be a MAYO key pair with whipped public map
$P^\ast$, and model $\shake$ as an ideal XOF to which the adversary makes
at most $Q_H$ (classical) queries. Call $y \in \Fsixteen^m$ an
\emph{admissible target with opening $w$} if either
(i) $y = \Cred(\kappa,b,\rho)$ with $w = (\kappa,b,\rho)$, or
(ii) $y = \Def(\ctx, \Cred(\kappa,b,\rho), t)$ with
$w = (\kappa,b,\rho,t)$ --- the two target languages the protocol signs,
under their respective domain tags. The adversary receives $\mathsf{pk}$
and adaptive (classical) access to an oracle that, given an admissible
target \emph{together with a valid opening}, returns an independently
sampled $\Spre(\mathsf{sk}, y)$; this mirrors the protocol, where the
issuer inverts only targets accompanied by a verified proof of opening
knowledge, and \emph{resamples} on repeated requests (only exact spend
retransmissions are answered from a cache, which the game models as no
query at all; preimages the issuer samples but discards after losing an
insertion race never leave the issuer and are not oracle replies). Let
$Q_S$ bound the total number of oracle calls and let $d \le Q_S$ be the
number of \emph{distinct} targets queried --- repeated calls on one target
consume $Q_S$ budget and yield fresh independent preimages, but do not
increase $d$. The adversary must output $d+1$ triples
$(y_j, w_j, \sigma_j)$ with the $y_j$ pairwise distinct admissible
targets, $w_j$ valid openings, and $P^\ast(\sigma_j) = y_j$. The
assumption is that every efficient adversary succeeds with probability
negligible in $\lambda$ (as a function of $Q_S$ and $Q_H$). Counting
distinct targets is essential: charging every call against the success
threshold would let $r$ resamplings of one target excuse a single forged
new target, which already violates fiscal soundness.

This is stronger and less studied than MAYO's signature unforgeability ---
the issuer here \emph{is} a preimage oracle. PoMFRIT~\cite{PoMFRIT}
formalizes an $(n,q)$ variant with $n$ \emph{random} targets, at most $q$
inversion calls, and $q+1$ distinct target indices for success; bridging
that game
to the adaptive, opening-accompanied, two-language version above (and
stating a QROM variant with quantum XOF access) is part of the outstanding
analysis, not a citation we inherit.
\end{assumption}

\begin{remark}[Hash modeling and adversary class]
\label{rem:xof}
The analysis models $\shake$ as an ideal XOF --- a \emph{prefix-consistent}
variable-output random oracle, so that reading $4m{+}256$ bits and reading
$4m$ bits of the same stream agree on their common prefix (ordinary
length-indexed random-oracle outputs do not automatically provide this) ---
for three distinct roles: the credential stream (hiding, collision and
preimage structure, suffix pseudorandomness given a prefix), the
GGM/vector-commitment PRG layer, and Fiat--Shamir. FIPS~202 standardizes
SHAKE but proves none of these properties; sponge indifferentiability is
the standard heuristic bridge. The claims of
Section~\ref{sec:security} target \emph{classical} PPT adversaries in this
ROM; the primitives are post-quantum candidates, but a QROM treatment
(quantum XOF access, quantum rewinding for extraction) is explicitly open,
so ``post-quantum'' describes the assumption class, not a proved quantum
security level.
\end{remark}

\section{The VOLE-ACT construction}
\label{sec:scheme}

\subsection{Credentials and nullifiers from one XOF stream}

Fix a 256-bit context $\ctx$ binding the issuer key (by hash of the expanded
public map), application domain, parameter set, VOLE profile, and protocol
version. The client samples $\kappa, \rho \gets \{0,1\}^{256}$ and, for base
balance $b \in \{0,\dots,2^{64}{-}1\}$, derives the stream
\[
X = \shake(\text{``credential''} \,\|\, \ctx \,\|\, \kappa \,\|\, \enc(b) \,\|\, \rho),
\quad
\Cred = X[0 : 4m], \quad \Null = X[4m : 4m{+}256].
\]
For MAYO$_2$, $\Cred$ is $4m = 256$ bits; its width as a collision domain
matters for fiscal security (Section~\ref{sec:security}).
Both values come from a \emph{single} sponge evaluation --- the message fits
one Keccak rate block --- so proving both costs one in-circuit permutation.
The commitment prefix $\Cred$ is revealed to the issuer exactly once (at
signing time); the nullifier suffix $\Null$ is revealed exactly once (at
spending time). Under the ideal-XOF modeling, the suffix is pseudorandom
given the prefix, which is what divorces the spend from the issuance.

\subsection{Two token formats and the settlement state machine}

A \emph{direct} token is $(\sigma, \kappa, b, \rho)$ with
$P^\ast(\sigma) = \Cred(\kappa,b,\rho)$ and effective balance $b$. A
\emph{deferred-return} token additionally carries an issuer-chosen return
$t$, with
\[
P^\ast(\sigma) \;=\; \Def\bigl(\ctx, \Cred(\kappa,b,\rho), t\bigr)
\;=\; \shake\bigl(\text{``deferred''} \,\|\, \ctx \,\|\,
\mathsf{pack16}(\Cred) \,\|\, \enc(t)\bigr)[0:4m],
\]
and effective balance $b + t$ (exact, non-wrapping). (The formal tuples
elide fixed metadata the implementation stores and
$\mathsf{VerifyToken}$ checks: the derived context, the credential-kind
tag, and the direct format's structurally zero top-up.) The nested hash
gives a
simple, domain-separated binding of both the base commitment and the return:
changing $t$ requires a fresh preimage or a target collision, and no
algebraic combiner (such as $\Cred + \iota(t)$) has to be analyzed for
malleability at all.

Spends are typed. An ordinary $\mathsf{Spend}$ consumes either format and
always outputs a direct token; $\mathsf{SpendDeferred}$ consumes
either format and outputs a deferred-return token. The client commits to a
fresh $(\kappa', \rho', b')$ \emph{before} the issuer chooses $t' \le s$, which is
precisely the case that cannot be expressed as a smaller net spend --- if the
return were known in advance, the client would simply spend less. All four
transitions carry distinct domain-separation tags end-to-end, so mode
confusion at the byte level cannot create an untyped path.

\subsection{Algorithms}
\label{sec:algorithms}

Figure~\ref{fig:algorithms} instantiates Definition~\ref{def:syntax}.
$\mathsf{pack16}$ packs a $\Fsixteen$-vector two nibbles per byte, first
element in the low nibble; all domain tags are ASCII strings under
prefix-free framing; $\Pi.\mathsf{Prove}/\mathsf{Verify}$ is the VOLEitH
argument of Section~\ref{sec:circuit} for the stated relation, with the
statement (all public values, tags, and $\ctx$) bound into Fiat--Shamir.

\begin{figure}[t]
\small
\begin{itemize}
  \item $\mathsf{Setup}(1^\lambda, \mathsf{app})$: run MAYO trapdoor
  generation for the chosen parameter set; expand the whipped forms; let
  $h_{\mathsf{pk}}$ be the domain-separated $\shake$ hash of the canonical
  row-major encoding of the expanded whipped forms of $P^\ast$; set
  \begin{align*}
  \ctx \gets \shake(&\text{``context''} \,\|\, \mathsf{frame}(\mathsf{app})
  \,\|\, h_{\mathsf{pk}}\\
  &\|\, \text{parameter and profile identifiers}
  \,\|\, \text{balance width})[0{:}256].
  \end{align*}
  Output $(\mathsf{sk}, \mathsf{pk}, \ctx)$.
  \item $\mathsf{Issue}$, client with $(\mathsf{pk}, b)$: sample
  $\kappa, \rho \gets \{0,1\}^{256}$; compute $\Cred$ from the credential
  stream; send $(b, \Cred, \pi)$ where $\pi \gets \Pi.\mathsf{Prove}$ for
  the relation $\Cred = \Cred(\kappa,b,\rho)$ with public $(b, \Cred,
  \ctx)$. Issuer: verify $\pi$ (and external authorization); return
  $\sigma \gets \Spre(\mathsf{sk}, \Cred)$. Client: accept the direct
  token $T = (\sigma, \kappa, b, \rho)$ iff $P^\ast(\sigma) = \Cred$.
  \item $\mathsf{Spend}$, client with $(\mathsf{pk}, T, s)$: sample fresh
  $(\kappa', \rho')$, set $b' = \mathsf{bal}(T) - s$, compute $\Cred'$ and
  $\Null$ from $T$'s stream; send $(s, \Null, \Cred', \pi)$ for the spend
  relation of Section~\ref{sec:relation} (typed for $T$'s kind, settlement
  tag ``spend''). Issuer: if the store already holds a record for $\Null$
  with the same request digest, return the stored response; on a digest
  conflict, reject. Otherwise verify $\pi$, sample
  $\sigma' \gets \Spre(\mathsf{sk}, \Cred')$, construct the candidate
  record $(\Null, \text{request digest}, \sigma')$, and \emph{atomically}
  insert it. If another record won the insertion race, compare digests:
  replay the winner if its digest matches this request, otherwise reject.
  Client:
  accept the direct token $(\sigma', \kappa', b', \rho')$ iff
  $P^\ast(\sigma') = \Cred'$.
  \item $\mathsf{SpendDeferred}$: as $\mathsf{Spend}$ with settlement tag
  ``deferred-return-spend'', except the issuer, after verifying $\pi$,
  first picks $t' \le s$, then samples
  $\sigma' \gets \Spre(\mathsf{sk}, \Def(\ctx, \Cred', t'))$, constructs
  the candidate record containing $(t', \sigma')$, and atomically inserts
  it; if another record won the race, it replays the winner --- including
  the winner's original $t'$ --- when digests match and rejects otherwise.
  Client: accept the deferred-return token
  $(\sigma', \kappa', b', \rho', t')$ iff $t' \le s$ and
  $P^\ast(\sigma') = \Def(\ctx, \Cred', t')$.
  \item $\mathsf{VerifyToken}(\mathsf{pk}, T)$: check that $T$'s stored
  context equals the context derived from $\mathsf{pk}$; that its
  credential kind and top-up obey the format's convention (a direct token
  carries no top-up); that the effective balance does not overflow;
  recompute $T$'s target ($\Cred$ or $\Def$) from its opening; and check
  $P^\ast(\sigma) = \text{target}$. (The anonymity game relies on honest
  clients performing \emph{all} of these checks.)
\end{itemize}
\caption{The VOLE-ACT algorithms. Every request and response carries the
credential-kind and settlement-mode tags; request digests bind the full
typed request bytes under $\ctx$.}
\label{fig:algorithms}
\end{figure}

\subsection{The spend relation}
\label{sec:relation}

To spend public amount $s$ from a direct token, the client reveals
$(s, \Null, \Cred')$ and proves knowledge of
$(\sigma, \kappa, b, \rho, \kappa', b', \rho')$ such that
\[
P^\ast(\sigma) = \Cred(\kappa,b,\rho), \qquad
\Null = \Null(\kappa,b,\rho), \qquad
b' + s = b, \qquad
\Cred' = \Cred(\kappa',b',\rho').
\]
For a deferred-input spend the first equation becomes
$P^\ast(\sigma) = \Def(\ctx, \Cred(\kappa,b,\rho), t)$ with hidden $t$, together with
the exact fold $b + t = e$ and $b' + s = e$. The balance equations are
\emph{exact 64-bit unsigned additions with zero final carry}, proven over
committed carry bits --- there is no modular wraparound to exploit, and
overspending is exactly the statement ``the final carry is 1,'' which the
circuit rejects. The issuer verifies, signs the fresh digest
($\sigma' \gets \Spre(\mathsf{sk}, \Cred')$, or the nested target for a
deferred settlement), and atomically stores the request digest and response
under $\Null$; exact retransmissions replay the stored response, so a
network failure cannot burn a balance.

\section{The proof circuit}
\label{sec:circuit}

The relation above is almost entirely SHAKE256: a direct-input spend proves
two hidden sponge evaluations (old stream, fresh stream), a deferred-input
spend proves three (the nested target costs one more). Everything else ---
the MAYO equation and the balance arithmetic --- is quadratic. This section
describes the three techniques that make the circuit small.

\subsection{Degree-16 Keccak checkpointing}
\label{sec:checkpoint}

Keccak-$f[1600]$'s round function is degree 2 (the $\chi$ step is the only
nonlinearity)~\cite{FIPS202}. The naive circuit commits all 1600 state bits
after every round: 24 rounds $\times$ 1600 witness bits, with degree-2
constraints between layers. But witness bits are the dominant cost in a
VOLE-style proof (each consumes a VOLE coordinate, enlarging both the
correction data and every leaf-PRG expansion), while raising the
\emph{degree} of the batched QuickSilver check is cheap: a maximum degree
$d$ costs $d$ published field elements and $d-1$ mask VOLEs \emph{in total}.

We therefore commit the state only every \emph{four} rounds. Between
checkpoints the circuit carries symbolic polynomial expressions: after
rounds $1,2,3,4$ the expressions have degree $2,4,8,16$, and the checkpoint
constraint asserts (per bit) that the degree-16 expression equals the next
committed state --- a degree-16 polynomial constraint, the largest the
instantiation accepts. This quarters the per-permutation witness from
$24 \times 1600$ to $6 \times 1600 = 9600$ bits. One permutation dominates
each hidden SHAKE evaluation, so a direct spend's witness is
$21{,}712$ bits and a deferred spend's $31{,}504$ --- versus roughly
$79{,}300$ and $117{,}900$ under per-round checkpointing. The prover-side
cost is the coefficient-vector products of the expression layer, about
$1.14$ million $\Ftag$ multiplications per permutation.

\subsection{The quadratic-system constraint for MAYO}
\label{sec:quadsys}

Verifying $P^\ast(\sigma) = y$ means checking $m = 64$ quadratic equations
\[
\sum_{r \le c} G_a[r,c]\; \sigma_r \sigma_c \;=\; y_a,
\qquad a \in [m],
\]
over the \emph{same} $\binom{325}{2} = 52{,}650$ products
$\sigma_r \sigma_c$. Materializing each product as a committed wire would
multiply the witness; instead the proof system supports a \emph{deferred
quadratic system}: the prover records the values and tags of every term
factor, and at challenge time the $m$ equations are folded into a single
QuickSilver degree-2 check by random weights $\varphi_a \in \Ftag$ drawn
from the transcript, with coefficients lifted through the embedding $\iota$.
An unsatisfied equation survives the fold except with probability
$2^{-\lambda}$. The committed signature nibbles enter as bit wires
($4 k_w n = 1296$ bits). The same mechanism folds the 64 quadratic carry
equations of each balance addition.

\subsection{Balance arithmetic in \texorpdfstring{$\Ftwo$}{GF(2)}}

Additions are proven bitwise with committed carry vectors:
$a_i + b_i + c_i = s_i$ linearly (over $\Ftwo$, addition is XOR --- an early
design error we caught was writing balance equations additively over the tag
field, where they say nothing about integers), and the carry recurrence
$c_{i+1} = a_i b_i + c_i(a_i + b_i)$ quadratically via the folded system.
Asserting the final carry to be zero makes every balance equation an exact
statement about 64-bit unsigned integers, so conservation is enforced
bit-exactly rather than modulo anything.

\section{Security analysis}
\label{sec:security}

We state the intended results as conditional claims against the definitions
of Section~\ref{sec:definitions}; no complete reduction is claimed, and
where the implementation's own analysis states sharper caveats, those
govern.

\begin{claim}[Fiscal soundness, conditional]
\label{claim:fiscal}
In the ideal-XOF model of Remark~\ref{rem:xof}, under
Assumption~\ref{ass:omp}, adaptive multi-theorem knowledge soundness
(extractability) of the VOLEitH argument for \emph{both} the issuance and
the spend relations, and a linearizable, non-rollback nullifier store,
VOLE-ACT satisfies Definition~\ref{def:fiscal}.
\end{claim}

\noindent\emph{Discussion and error terms.}
Conditionally on extraction, every accepted operation yields an opening
and a MAYO preimage for an admissible target, correct nullifier
derivation, and exact balance arithmetic; over-redemption then requires
either one more admissible preimage than the issuer produced
(Assumption~\ref{ass:omp}) or a \emph{target collision}. The collision
cases are: two credential-stream openings with equal $\Cred$; two
deferred wrappers with equal $\Def$ output; and a cross-domain collision
$\Cred = \Def(\cdot)$ --- the domain tags separate the hash inputs, but
all three remain generic collision events in the same $4m$-bit output
space and must be counted. A fourth, operational collision event: the
retry store retains a 256-bit \emph{request digest} rather than the full
request, so exact-retry semantics additionally assume collision
resistance of that digest (or full-request comparison), and the redeemed
service itself --- not merely the token response --- must be tied
idempotently to the first durable record. Issuance soundness matters because
Assumption~\ref{ass:omp} feeds the oracle only opening-accompanied
targets: without it, a malicious issuance request could obtain a preimage
for an unopened target. The dominant known terms and generic ceilings
include (this is not yet a complete advantage expression --- proof-attempt
counts, $Q_H$ factors, vector-commitment and consistency terms, and
composition loss are unquantified):
\begin{itemize}
  \item The degree-16 batched QuickSilver check contributes up to
  $17/2^{128} \approx 2^{-123.9}$ per proof attempt, before
  vector-commitment, consistency-hash, Fiat--Shamir, and composition terms.
  \item The credential digest is a collision domain of only $4m = 256$
  bits. Two openings $(\kappa,b,\rho) \ne (\kappa',b',\rho')$ with the same
  prefix $\Cred$ let the \emph{one} issuer-supplied preimage $\sigma$ be
  presented under both --- their suffix nullifiers will generally differ ---
  double-spending, and with distinct balances creating value. This is
  generic collision search: about $2^{128}$ classically, and query
  complexity $\Theta(2^{256/3}) \approx 2^{85.3}$ for an ideal quantum
  collision adversary~\cite{BHT} (under BHT's demanding memory model).
  Deployments requiring a larger quantum collision margin need a wider
  digest, hence a larger $m$.
\end{itemize}
Honest double spends are prevented operationally: a repeated credential
reveals the same deterministic nullifier, whose conflicting reuse the
store refuses while exact retransmissions are replayed from the stored
record --- the atomic retry semantics that also make honest
retransmission safe.

\begin{claim}[Spend anonymity, conditional]
\label{claim:anon}
In the ideal-XOF model of Remark~\ref{rem:xof}, assuming the VOLEitH
argument is adaptive multi-theorem non-interactive zero knowledge for the
chosen-key relation (i.e., against maliciously formed but canonically
parsed public keys, in the ROM), VOLE-ACT satisfies
Definition~\ref{def:anon}; the claim does not depend on any MAYO
assumption.
\end{claim}

\noindent\emph{Discussion.}
A spend reveals $(s, \Null, \Cred', \text{proof})$. The intended argument:
the compiled argument is NIZK zero-knowledge in the sense above (the
$2\lambda$-bit per-proof salt is multi-instance \emph{hardening}, not by
itself a theorem upgrading honest-verifier ZK to this property); $\Cred'$
hides its opening under the fresh 256-bit nonce $\rho'$; and $\Null$ is
the unrevealed suffix of an XOF stream whose prefix the issuer saw at
issuance, pseudorandom given the prefix in the ideal-XOF model. None of
these steps is currently backed by a proof for this exact composition, so
the claim is conditional on all three. Its MAYO-independence is the design's compartmentalization: a
trapdoor recovery or forgery does not help the distinguisher in
Definition~\ref{def:anon}. Outside the game, deployments leak metadata the
definition deliberately excludes: spend amounts are public; direct-input
and deferred-input proofs differ substantially in size and partition the
anonymity set, as do credential kind, settlement mode, request length,
timing, network identity, and retry behavior.

\paragraph{Multi-instance hardening.}
Every PRG and commitment call in the tree layer binds salt and position
(after~\cite{OneTree}), preventing the known precomputation and
batch-amortization attacks on the 128-bit seeds; a concrete multi-user bound
still carries adversary-instance-dependent terms. The wide consistency hash
removes the $2^{-h}$ per-chunk cheating strategy. Domain tags separate every
hash use; all encodings are canonical and rejected on any alternate
serialization.

\section{Parameters and evaluation}
\label{sec:performance}

The construction is implemented as a Rust research prototype (five crates:
binary fields, GGM vector commitments, the VOLEitH proof system, MAYO, and
the protocol). Table~\ref{tab:sizes} gives wire sizes; tokens are
profile-independent and only proof-carrying requests grow with the
low-latency profiles. On one Apple M4 Pro, a direct spend proves in
19--20\,ms and verifies-and-signs in 6.5--8\,ms across profiles (issuance:
8--9\,ms and 3--4\,ms; deferred-input spends roughly $1.4\times$ a direct
spend). Figures are single-operation latencies on an idle machine. The
compact profile's proving penalty over low-latency is $\approx$6--7\%
while its proofs are $3.8\times$ smaller. Implementation techniques,
optimization methodology, and full per-profile measurements are documented
in the repository,
\url{https://github.com/SamuelSchlesinger/vole-act}
(\texttt{docs/IMPLEMENTATION.md}, \texttt{docs/BENCHMARKS.md}; the
measurements in this paper correspond to commit \texttt{65248c8}).

\begin{table}[h]
\centering
\caption{Wire sizes (bytes), MAYO$_2$, $\lambda = 128$.}
\label{tab:sizes}
\begin{tabular}{lrrr}
\toprule
Object & compact & balanced & low-latency \\
& $(\tau,h){=}(16,8)$ & $(32,4)$ & $(64,2)$ \\
\midrule
Token (either format) & 283 & 283 & 283 \\
Issue request & 29\,750 & 55\,286 & 106\,358 \\
Spend request (direct input) & 52\,990 & 101\,726 & 199\,198 \\
Spend request (deferred input) & 72\,574 & 140\,894 & 277\,534 \\
Issue / spend response & 171 / 179 & 171 / 179 & 171 / 179 \\
Public key (expanded map) & 106\,319 & 106\,319 & 106\,319 \\
\bottomrule
\end{tabular}
\end{table}

\section{Related work}

VOLE-based designated-verifier ZK begins with
Wolverine~\cite{Wolverine} and Mac'n'Cheese~\cite{MacNCheese};
QuickSilver~\cite{QuickSilver} gives the degree-$d$ batched check we
generalize. VOLE-in-the-Head~\cite{VOLEitH} removes the designated verifier
and underlies the FAEST signature candidate~\cite{FAEST}, whose engineering
(GGM trees, salting, consistency checking) we follow, with the hardening of
\cite{OneTree}. MAYO~\cite{Beullens21,MAYOspec} descends from unbalanced
oil-and-vinegar~\cite{UOV}; \cite{Beullens22} is the cautionary tale for the
assumption class. The closest post-quantum
relative is PoMFRIT~\cite{PoMFRIT}, a \emph{blind-signature} scheme that
likewise combines VOLE-in-the-Head proofs of SHA-3-family circuits with the
MAYO trapdoor and analyzes the one-more-preimage property such issuers
require --- an instructive contrast: PoMFRIT pursues the blindness route
with the same toolbox, while VOLE-ACT's commit-then-sign design avoids
blindness and adds stateful balances, typed settlement, and deferred
returns. Anonymous tokens and credentials span
blind signatures~\cite{Chaum82}, CL signatures~\cite{CL01},
keyed-verification credentials from algebraic MACs~\cite{CMZ14}, and
deployed unit-token systems~\cite{PrivacyPass}; VOLE-ACT is a post-quantum
stateful-balance member of this family, instantiating the
Katz--Schlesinger design~\cite{KS}.

\section{Open problems}

(1)~A complete security reduction: formalizing
Definitions~\ref{def:fiscal}--\ref{def:anon} fully (concurrency, chains,
adaptive corruptions) and proving Claims~\ref{claim:fiscal}
and~\ref{claim:anon} in the QROM, including a precise formulation of
Assumption~\ref{ass:omp} and its relation to MAYO's standard security.
(2)~A structured, non-materialized QuickSilver check for the whipped MAYO
equation, removing the $O(m (k_w n)^2)$ expanded-form table and enabling the
larger MAYO parameter sets (whose wider digests also raise the quantum
collision ceiling).
(3)~Hashing the compact public-key encoding (rather than the expanded forms)
into the context --- a transcript-breaking cleanup best done before any
format freeze.
(4)~Aggregating or compressing spend proofs; at 53\,KiB the compact profile
is deployable server-side but remains the dominant bandwidth cost.
(5)~Hidden spend amounts, which would require in-circuit range checks and
re-open the balance-width trade-off.

\begin{thebibliography}{99}\small

\bibitem{Beullens21}
W.~Beullens.
\emph{MAYO: Practical Post-Quantum Signatures from Oil-and-Vinegar Maps}.
SAC 2021.

\bibitem{Beullens22}
W.~Beullens.
\emph{Breaking Rainbow Takes a Weekend on a Laptop}.
CRYPTO 2022.

\bibitem{MAYOspec}
W.~Beullens, F.~Campos, S.~Celi, B.~Hess, M.~J.~Kannwischer.
\emph{MAYO: Algorithm Specification (Round-2 document, February 5, 2025)}.
NIST PQC Additional Digital Signatures. This work pins the Round-2
specification; MAYO advanced to Round 3 in May 2026.
\url{https://pqmayo.org/resources/}.

\bibitem{VOLEitH}
C.~Baum, L.~Braun, C.~Delpech de Saint Guilhem, M.~Kloo{\ss}, E.~Orsini,
L.~Roy, P.~Scholl.
\emph{Publicly Verifiable Zero-Knowledge and Post-Quantum Signatures from
VOLE-in-the-Head}.
CRYPTO 2023.

\bibitem{FAEST}
C.~Baum, W.~Beullens, L.~Braun, C.~Delpech de Saint Guilhem, M.~Kloo{\ss},
C.~Majenz, S.~Mukherjee, E.~Orsini, S.~Ramacher, C.~Rechberger, L.~Roy,
P.~Scholl.
\emph{FAEST: Algorithm Specification, Version 2.0 (Round-2 document)}.
NIST PQC Additional Digital Signatures. This work follows the Round-2
(v2.0) design; FAEST advanced to Round 3 in May 2026.
\url{https://faest.info}.

\bibitem{OneTree}
C.~Baum, W.~Beullens, S.~Mukherjee, E.~Orsini, S.~Ramacher, C.~Rechberger,
L.~Roy, P.~Scholl.
\emph{One Tree to Rule Them All: Optimizing GGM Trees and OWFs for
Post-Quantum Signatures}.
ASIACRYPT 2024.

\bibitem{QuickSilver}
K.~Yang, P.~Sarkar, C.~Weng, X.~Wang.
\emph{QuickSilver: Efficient and Affordable Zero-Knowledge Proofs for
Circuits and Polynomials over Any Field}.
ACM CCS 2021.

\bibitem{Wolverine}
C.~Weng, K.~Yang, J.~Katz, X.~Wang.
\emph{Wolverine: Fast, Scalable, and Communication-Efficient Zero-Knowledge
Proofs for Boolean and Arithmetic Circuits}.
IEEE S\&P 2021.

\bibitem{MacNCheese}
C.~Baum, A.~J.~Malozemoff, M.~B.~Rosen, P.~Scholl.
\emph{Mac'n'Cheese: Zero-Knowledge Proofs for Boolean and Arithmetic
Circuits with Nested Disjunctions}.
CRYPTO 2021.

\bibitem{SoftSpoken}
L.~Roy.
\emph{SoftSpokenOT: Quieter OT Extension from Small-Field Silent VOLE in the
Minicrypt Model}.
CRYPTO 2022.

\bibitem{GGM86}
O.~Goldreich, S.~Goldwasser, S.~Micali.
\emph{How to Construct Random Functions}.
Journal of the ACM 33(4), 1986.

\bibitem{UOV}
A.~Kipnis, J.~Patarin, L.~Goubin.
\emph{Unbalanced Oil and Vinegar Signature Schemes}.
EUROCRYPT 1999.

\bibitem{FIPS202}
NIST.
\emph{SHA-3 Standard: Permutation-Based Hash and Extendable-Output
Functions}.
FIPS PUB 202, 2015.

\bibitem{BHT}
G.~Brassard, P.~H{\o}yer, A.~Tapp.
\emph{Quantum Cryptanalysis of Hash and Claw-Free Functions}.
LATIN 1998. arXiv:quant-ph/9705002.

\bibitem{Chaum82}
D.~Chaum.
\emph{Blind Signatures for Untraceable Payments}.
CRYPTO 1982.

\bibitem{CL01}
J.~Camenisch, A.~Lysyanskaya.
\emph{An Efficient System for Non-transferable Anonymous Credentials with
Optional Anonymity Revocation}.
EUROCRYPT 2001.

\bibitem{CMZ14}
M.~Chase, S.~Meiklejohn, G.~Zaverucha.
\emph{Algebraic MACs and Keyed-Verification Anonymous Credentials}.
ACM CCS 2014.

\bibitem{PrivacyPass}
A.~Davidson, I.~Goldberg, N.~Sullivan, G.~Tankersley, F.~Valsorda.
\emph{Privacy Pass: Bypassing Internet Challenges Anonymously}.
Proceedings on Privacy Enhancing Technologies 2018(3), 164--180.

\bibitem{PoMFRIT}
C.~Baum, M.~Beckmann, W.~Beullens, S.~Mukherjee, C.~Rechberger.
\emph{Concretely Efficient Blind Signatures Based on VOLE-in-the-Head
Proofs and the MAYO Trapdoor (PoMFRIT)}.
USENIX Security 2026. IACR ePrint 2026/109.

\bibitem{KS}
J.~Katz, S.~Schlesinger.
\emph{Anonymous Credit Tokens}.
Design document and Rust implementation,
\url{https://github.com/SamuelSchlesinger/anonymous-credit-tokens}.

\end{thebibliography}

\end{document}
